\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-18 paper/experiments.tex
paper: format queries
paper: added acs example to show base table imputation infeasible

@@

\begin{table*}
\todo{clean up formatting here}
\centering
 \begin{subtable}{\linewidth}
  \input{queries-cdc}
  \caption{Queries on CDC data}
  \label{fig:queries-cdc}
 \end{subtable}
 ~
 \begin{subtable}{\linewidth}
 \input{queries-fcc}
 \caption{Queries on FCC data}
 \label{fig:queries-fcc}
 \end{subtable}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table*}

@@

\todo{Add timing comparison to ACS table since that should take longer than base on the data we have}

>>>>

For our final experiment, we introduce a simple aggregate query over data from the American Community Survey (ACS), which
provides a number of public data sets collected by the U.S. Census Bureau.
We used a cleaned version of the 2012 Public Use Microdata Sample (PUMS) data kindly provided by the authors of~\cite{akande2015empirical}.
Given that the data had been cleaned, we uniformly introduced missing values across 40 percent of the values. The final dataset consists
of 671,153 rows and 37 integer columns.

@@

\begin{table*}
\centering
 \begin{subtable}{\linewidth}
  \input{queries-cdc}
  \caption{Queries on CDC data}
  \label{fig:queries-cdc}
 \end{subtable}
 ~
 \begin{subtable}{\linewidth}
 \input{queries-fcc}
 \caption{Queries on FCC data}
 \label{fig:queries-fcc}
 \end{subtable}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table*}

@@

In many cases, applying the imputation step at the base table simply is not an option. To illustrate the increasing difficulty of such an approach
as datasets scale, we used a simple aggregate query over the ACS dataset (Figure~\ref{query-acs}). Applying the imputation operation to the base table
is extremely expensive, in our case the process did not terminate within 20 minutes. In contrast, \ProjectName{} executes a quality-optimized version
in 9 seconds and a runtime-optimized version in 1 second. This highlights the potential benefit of using our system for early data exploration.

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is unfeasible (did not terminate within 20min). \ProjectName's
quality-optimized and performance-optimized query execute in 9 seconds and 1 second, respectively.
}
\label{query-acs}
\end{figure}
